Qualifying Report

### 2018-05-14 QualifyingReport/QualifyingReport.tex
fixed conflicts
added more searches for literature review

	\subsection{Literature Review - April 2018 to July 2018}
	A literature review was carried out from several perspectives in order to understand both an applied and theoretical perspective. Thus a search for papers was conducted in both the psychology and computer science domains, as well as papers which intersected these areas and were relevant to this particular problem.

	\subsection{Skills development - April 2018 to March 2019}
	\textbf{IS-4001 Research Skills and Professional Development Module - Aston University - 3rd May, 10th May, 16th May - 45 Hours} \newline
	\par
	Day 1 consisted of an introduction to the module (IS4001), a rough guide to how to start a PhD and a look at how to conduct and write a literature review. This looked at the concept of a PhD and the meaning of original research. This also talked about the supervisor relationship and understanding the role of the supervisor in the PhD. In addition, we explored the idea of our expectations around supervision. We then went on to look at what skills, qualities and attitudes are necessary to be a good researcher including the idea of what consitutes ethical research and finally we looked at the obstacles to progress on a PhD and what we can do as students.
	\newline
	\par
	In the afternoon, we looked at how a way of conducting a literature review. This talked about what a literature review is, along with the different types of literature review (Narrative, Systematic and Meta-Analysis). We talked about the function of a literature review, and how this fits in with the writing up of a thesis. We then explored the stages that the literature review process contains, from defining the scope of the research, to coming up with a plan on how to collect sources of information to synthesising and reporting the findings of the review. This part of the lecture looked in detail at each of these areas and included some examples to put the theory of the literature into context. Finally, we talked about the the process of a literature review in the context of the written assignment. 
	\newline
	\par
	\textbf{Alexa Skills Training Day - Amazon - May 9th 2018 - 7 Hours}
	\newline
	\par
	Test
	\newline
	\textbf{Deep Learning Online Course - deeplearning.ai - Dates - 70 Hours}
	Summary Here

>>>>

	\subsection{Literature Review - April 2018 to July 2018}
	A literature review was carried out from several perspectives in order to understand both an applied and theoretical perspective. Thus a search for papers was conducted in both the psychology and computer science domains, as well as papers which intersected these areas and were relevant to this particular problem.
	\newline
	SEARCH - ProQuest (PsychArticles) - Search Terms (Language AND Decline AND DEMENTIA) - 1484 Results
	SEARCH - ProQuest (PsychArticles) - Search Terms (Language AND Decline AND DEMENTIA AND Speech) - 486 Results
	SEARCH - Web Of Science - Search Terms (Language AND Decline AND DEMENTIA AND Speech) - 151 Results
	SEARCH - Web of Science - Search Terms (Language AND Decline AND DEMENTIA) - 1207 Results
	SEARCH - Scopus - Search Terms (Language AND Decline AND DEMENTIA AND Speech) - 91 Results 
	SEARCH - Scopus - Search Terms (Languge AND DEMENTIA AND Decline) - 791 Results

	\subsection{Skills development - April 2018 to March 2019}
	\textbf{IS-4001 Research Skills and Professional Development Module - Aston University - 3rd May, 10th May, 16th May - 45 Hours} \newline
	\par
	Day 1 consisted of an introduction to the module (IS4001), a rough guide to how to start a PhD and a look at how to conduct and write a literature review. This looked at the concept of a PhD and the meaning of original research. This also talked about the supervisor relationship and understanding the role of the supervisor in the PhD. In addition, we explored the idea of our expectations around supervision. We then went on to look at what skills, qualities and attitudes are necessary to be a good researcher including the idea of what consitutes ethical research and finally we looked at the obstacles to progress on a PhD and what we can do as students.
	\newline
	\par
	In the afternoon, we looked at how a way of conducting a literature review. This talked about what a literature review is, along with the different types of literature review (Narrative, Systematic and Meta-Analysis). We talked about the function of a literature review, and how this fits in with the writing up of a thesis. We then explored the stages that the literature review process contains, from defining the scope of the research, to coming up with a plan on how to collect sources of information to synthesising and reporting the findings of the review. This part of the lecture looked in detail at each of these areas and included some examples to put the theory of the literature into context. Finally, we talked about the the process of a literature review in the context of the written assignment. 
	\newline
	\par
	Test
	\newline
	\par
	\textbf{Alexa Skills Training Day - Amazon - May 9th 2018 - 7 Hours}
	\newline
	\par
	Test
	\newline
	\textbf{Deep Learning Online Course - deeplearning.ai - Dates - 70 Hours}
	Summary Here
